Continuations via Negative Information Flow

### 2012-02-13 dual.tex
added neg circuits
added function dispatch

>>>>

Actually this is possible. Consider two functions {{f : b1 <-> b2}}
and {{g : b1 <-> b2}}. A value of type {{bool}} is sufficient to
discriminate them. Hence the {{boo}} is the first class representation
of the functions and can be thought of as the address of the function.

\begin{center}
  \includegraphics{diagrams/dispatch.pdf}
\end{center}

\item It is not fair to say that negative types flow backwards. The
  following circuits are valid in {{langRevEE}}. It is however proper
  to say that for any type {{b}} that flows in a direction, the type
  {{-b}} flows in the reverse direction.

\begin{center}
  \includegraphics{diagrams/neg_circuit1.pdf}
\end{center}

\begin{center}
  \includegraphics{diagrams/neg_circuit2.pdf}
\end{center}
